\thetitle

### 2021-07-24 writing/why-rational-methodology.tex
Small grammar + typo fixes, and minor wording changes
Changes to satisfy the publisher

Every time the rational programmer succeeds, it is validation for programming
language researchers. It shows how their theorems and slogans help
programmers. The example of blame assignment mechanisms makes this point
clearly. A blame-assignment mechanism provides information that, according to
programming language research, points toward the source of the problem.

>>>>

\vspace{1.5em}
\textbf{How to Turn the Idea of the Rational Programmer into a Methodology.}
Every time the rational programmer succeeds, it is validation for programming
language researchers. It shows how their theorems, slogans, and tools help
programmers. The example of blame assignment mechanisms makes this point
clearly. A blame-assignment mechanism provides information that, according to
programming language research, points toward the source of the problem.
